From textual to structured Web API Descriptions\\ \large Knowledge Discovery and Data Mining Seminar 2017

### 2017-08-29 Paper/Paper_KDD.tex
citations und Hans Teil
citations und Hans Teil

\section{Datasets and Crawling}
\piccaption{Amount of working links in Programmable Web} 
\parpic[r]{\includegraphics[width=1.5in]{img/pie.png}} 
Prior to our research and development, we looked for suitable datasets with good quality. There was not much research done in this field, therefore we had to look for different alternatives, which will be described in the following Sections. Section II.A describes the Linked Web API dataset and the issues. Section II.B deals with the dataset crawled from Programmable Web  \footnote[1]{https://www.programmableweb.com} and Section II.C shows an alternative way to get data from Google.

@@

\section{Manual Clustering}

>>>>

\section{Datasets and Crawling}
%rechtsbündige grafik
%\piccaption{Amount of working links in Programmable Web} 
%\parpic[r]{\includegraphics[width=1.5in]{img/pie.png}} 
Prior to our research and development, we looked for suitable datasets with good quality. There was not much research done in this field, therefore we had to look for different alternatives, which will be described in the following Sections. Section II.A describes the Linked Web API dataset and the issues. Section II.B deals with the dataset crawled from Programmable Web  \footnote[1]{https://www.programmableweb.com} and Section II.C shows an alternative way to get data from Google.
\begin{figure}[!t]
\centering
\includegraphics[width= 2in]{img/pie.png}
\caption{Amount of working links in Programmable Web}
\label{fig_sim}
\end{figure}

@@

\section{Manual Clustering}
To be able to assess the quality of our trained clusters, we decided to manually create clusters and only evaluate (in Section V) on those manually clustered APIs. With that, we could test different clustering parameters described in Section IV and choose the best parameters. We split the dataset according to the existing categories and took the five tags: “Messaging”, “Payments”, “eCommerce”, “Mapping” and “Finance”, since they contained most of the APIs. Based on the descriptions we clustered those APIs manually, so that we receive about 30 APIs per cluster. After 2-3 days of processing, we had 26 manually created clusters with 962 APIs.
